quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-17 paper-quollr.tex
Add hex coord generation from scratch

\begin{verbatim}
num_bins_x <- calculate_effective_x_bins(.data = s_curve_noise_umap, x = "UMAP1", cell_area = 1)
num_bins_x
\end{verbatim}

\begin{verbatim}
#> [1] 6
\end{verbatim}

\begin{verbatim}
shape_val <- calculate_effective_shape_value(.data = s_curve_noise_umap, x = "UMAP1", y = "UMAP2")
shape_val
\end{verbatim}

\begin{verbatim}
#> [1] 2.019414
\end{verbatim}

\begin{verbatim}
num_bins_y <- calculate_effective_y_bins(.data = s_curve_noise_umap, x = "UMAP1", y = "UMAP2", shape_val = 1.833091, num_bins_x = num_bins_x)
num_bins_y
\end{verbatim}

\begin{verbatim}
#> [1] 12
\end{verbatim}

@@

\begin{verbatim}
cell_area <- 1
cell_diameter <- sqrt(2 * cell_area / sqrt(3))

hex_size <- cell_diameter/2

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-8-1.pdf}

@@

\begin{verbatim}
#> Rows: 72
#> Columns: 2
#> $ x <dbl> -3.5390002, -2.9126765, -3.5390002, -2.9126765, -3.5390002, -2.91267~
#> $ y <dbl> -6.0111830, -4.9111506, -3.8111182, -2.7110858, -1.6110534, -0.51102~
\end{verbatim}

@@

\begin{verbatim}
hex_grid <- gen_hex_coordinates(all_centroids_df)
glimpse(hex_grid)
\end{verbatim}

\begin{verbatim}
#> Rows: 432
#> Columns: 3
#> $ x  <dbl> -2.912676, -2.912676, -3.539000, -4.165324, -4.165324, -3.539000, -~
#> $ y  <dbl> -5.645998, -6.376368, -6.741553, -6.376368, -5.645998, -5.280813, -~
#> $ id <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4~
\end{verbatim}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-12-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-18-1.pdf}

@@

\begin{verbatim}
#> # A tibble: 20 x 4
#>         x      y hexID std_counts
#>     <dbl>  <dbl> <int>      <dbl>
#>  1 -2.91  -4.91      7      0.5  
#>  2 -3.54  -3.81     13      0.5  
#>  3 -2.29  -6.01      2      0.5  
#>  4 -1.66  -4.91      8      0.75 
#>  5 -2.29  -3.81     14      0.5  
#>  6 -1.03  -3.81     15      0.375
#>  7 -0.407 -2.71     21      0.125
#>  8 -1.03  -1.61     27      0.125
#>  9  0.219 -1.61     28      1    
#> 10  0.845 -0.511    34      0.625
#> 11  0.845  1.69     46      0.125
#> 12  0.845  3.89     58      0.625
#> 13  0.219  4.99     64      0.125
#> 14  0.845  6.09     70      0.375
#> 15  1.47   0.589    41      1    
#> 16  1.47   2.79     53      0.125
#> 17  2.10   3.89     59      0.625
#> 18  1.47   4.99     65      0.5  
#> 19  2.10   6.09     71      0.375
#> 20  2.72   4.99     66      0.5
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 72
#> Columns: 2
#> $ x <dbl> -3.2700000, -2.6436763, -3.2700000, -2.6436763, -3.2700000, -2.64367~
#> $ y <dbl> -5.7400000, -4.6399676, -3.5399352, -2.4399028, -1.3398704, -0.23983~
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 432
#> Columns: 3
#> $ x  <dbl> -2.643676, -2.643676, -3.270000, -3.896324, -3.896324, -3.270000, -~
#> $ y  <dbl> -5.3748152, -6.1051848, -6.4703696, -6.1051848, -5.3748152, -5.0096~
#> $ id <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4~
\end{verbatim}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-25-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-31-1.pdf}

@@

\begin{verbatim}
#> # A tibble: 21 x 4
#>         x     y hexID std_counts
#>     <dbl> <dbl> <int>      <dbl>
#>  1 -3.27  -5.74     1      0.286
#>  2 -2.64  -4.64     7      0.571
#>  3 -3.27  -3.54    13      0.714
#>  4 -2.02  -5.74     2      0.857
#>  5 -1.39  -4.64     8      0.429
#>  6 -2.02  -3.54    14      0.286
#>  7 -0.765 -3.54    15      0.429
#>  8 -0.138 -2.44    21      0.143
#>  9 -0.765 -1.34    27      0.286
#> 10  0.488 -1.34    28      1    
#> # i 11 more rows
\end{verbatim}

@@

@@

@@

\begin{verbatim}
trimesh_gr <- colour_long_edges(.data = distance, benchmark_value = benchmark,
                                triangular_object = tr1_object, distance_col = distance)

@@

\begin{verbatim}
trimesh_removed <- remove_long_edges(.data = distance, benchmark_value = benchmark,
                                     triangular_object = tr1_object, distance_col = distance)
trimesh_removed
\end{verbatim}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-39-1.pdf}

@@

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-42-1.pdf}

@@

\begin{verbatim}
#> Calculating PHATE...
#>   Running PHATE on 824 observations and 8 variables.
#>   Calculating graph and diffusion operator...
#>     Calculating KNN search...
#>     Calculating affinities...
#>   Calculated graph and diffusion operator in 0.01 seconds.
#>   Calculating optimal t...
#>     Automatically selected t = 22
#>   Calculated optimal t in 0.39 seconds.
#>   Calculating diffusion potential...
#>   Calculated diffusion potential in 0.32 seconds.
#>   Calculating metric MDS...
#>   Calculated metric MDS in 8.83 seconds.
#> Calculated PHATE in 9.55 seconds.
\end{verbatim}

@@

\begin{verbatim}
num_bins_x <- calculate_effective_x_bins(.data = tSNE_data, x = "tSNE1", cell_area = 1)
num_bins_x <- 13
\end{verbatim}

\begin{verbatim}
shape_val <- calculate_effective_shape_value(.data = tSNE_data, x = "tSNE1", y = "tSNE2")
shape_val
\end{verbatim}

\begin{verbatim}
#> [1] 1.13882
\end{verbatim}

\begin{verbatim}
num_bins_y <- calculate_effective_y_bins(.data = tSNE_data, x = "tSNE1", y = "tSNE2", shape_val = 0.8417289, num_bins_x = num_bins_x)
num_bins_y
\end{verbatim}

\begin{verbatim}
#> [1] 14
\end{verbatim}

@@

df_with_std_counts <- compute_std_counts(nldr_df = s_curve_noise_umap_with_id)

@@

\begin{verbatim}
#> # A tibble: 21 x 4
#>        x     y hexID std_counts
#>    <dbl> <dbl> <int>      <dbl>
#>  1 -27.7 -34.8     1      0.286
#>  2 -25.4 -30.1    14      0.286
#>  3 -27.7 -25.4    27      0.286
#>  4 -25.4 -20.7    40      0.286
#>  5 -27.7 -16.0    53      0.429
#>  6 -25.4 -11.3    66      0.143
#>  7 -23.2 -34.8     2      0.857
#>  8 -20.9 -30.1    15      0.429
#>  9 -23.2 -25.4    28      1    
#> 10 -20.9 -20.7    41      0.714
#> # i 11 more rows
\end{verbatim}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
Xie, Yihui. 2015. \emph{Dynamic Documents with {R} and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{https://yihui.name/knitr/}.

>>>>

\begin{verbatim}
num_bins_x <- calculate_effective_x_bins(.data = s_curve_noise_umap, x = "UMAP1", hex_size = NA)
num_bins_x
\end{verbatim}

\begin{verbatim}
#> [1] 4
\end{verbatim}

\begin{verbatim}
num_bins_y <- calculate_effective_y_bins(.data = s_curve_noise_umap, y = "UMAP2", hex_size = NA)
num_bins_y
\end{verbatim}

\begin{verbatim}
#> [1] 8
\end{verbatim}

@@

\begin{verbatim}
cell_area <- 1

hex_size <- sqrt(2 * cell_area / sqrt(3))

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

@@

\begin{verbatim}
#> Rows: 32
#> Columns: 2
#> $ x <dbl> -3.8076427, -2.6742223, -3.8076427, -2.6742223, -3.8076427, -2.67422~
#> $ y <dbl> -6.2798254, -4.4744481, -2.6690708, -0.8636935, 0.9416838, 2.7470611~
\end{verbatim}

@@

\begin{verbatim}
hex_grid <- gen_hex_coordinates(all_centroids_df, hex_size = NA)
glimpse(hex_grid)
\end{verbatim}

\begin{verbatim}
#> Rows: 192
#> Columns: 3
#> $ x  <dbl> -2.674222, -2.674222, -3.807643, -4.941063, -4.941063, -3.807643, -~
#> $ y  <dbl> -5.6804828, -6.8791681, -7.4785108, -6.8791681, -5.6804828, -5.0811~
#> $ id <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4~
\end{verbatim}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-10-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-16-1.pdf}

@@

@@

\begin{verbatim}
#>             x          y hexID std_counts
#> 1  -2.6742223 -4.4744481     5     1.0000
#> 2  -1.5408019 -6.2798254     2     0.3125
#> 3  -0.4073814 -4.4744481     6     0.0625
#> 4  -1.5408019 -2.6690708    10     0.2500
#> 5  -0.4073814 -0.8636935    14     0.5000
#> 6   0.7260390 -2.6690708    11     0.1250
#> 7   1.8594594 -0.8636935    15     0.1875
#> 8   0.7260390  0.9416838    19     0.6250
#> 9   1.8594594  2.7470611    23     0.2500
#> 10  0.7260390  4.5524384    27     0.5625
#> 11  1.8594594  6.3578158    31     0.3750
#> 12  2.9928798  4.5524384    28     0.4375
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 32
#> Columns: 2
#> $ x <dbl> -3.5386425, -2.4052221, -3.5386425, -2.4052221, -3.5386425, -2.40522~
#> $ y <dbl> -6.0086424, -4.2032651, -2.3978878, -0.5925105, 1.2128668, 3.0182441~
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 192
#> Columns: 3
#> $ x  <dbl> -2.405222, -2.405222, -3.538643, -4.672063, -4.672063, -3.538643, -~
#> $ y  <dbl> -5.409299776, -6.607985117, -7.207327787, -6.607985117, -5.40929977~
#> $ id <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4~
\end{verbatim}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-23-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-29-1.pdf}

@@

@@

\begin{verbatim}
#>             x          y hexID std_counts
#> 1  -3.5386425 -6.0086424     1 0.21428571
#> 2  -2.4052221 -4.2032651     5 1.00000000
#> 3  -1.2718017 -6.0086424     2 0.42857143
#> 4  -0.1383812 -4.2032651     6 0.07142857
#> 5  -1.2718017 -2.3978878    10 0.21428571
#> 6  -0.1383812 -0.5925105    14 0.50000000
#> 7   0.9950392 -2.3978878    11 0.28571429
#> 8   2.1284596 -0.5925105    15 0.14285714
#> 9   0.9950392  1.2128668    19 0.64285714
#> 10  2.1284596  3.0182441    23 0.35714286
#> 11  0.9950392  4.8236214    27 1.00000000
#> 12  2.1284596  6.6289988    31 0.07142857
#> 13  3.2618800  4.8236214    28 0.42857143
\end{verbatim}

@@

\begin{verbatim}
## As an option first quantile considered as a default
benchmark_to_rm_lwd_hex <- quantile(df_bin_centroids$std_counts)[2] + 0.01

## To identify low density hexagons
df_bin_centroids_low <- df_bin_centroids |>
  dplyr::filter(std_counts <= benchmark_to_rm_lwd_hex)

## To identify low-density hexagons needed to remove by investigating neighbouring mean density
identify_rm_bins <- find_low_density_hexagons(df_bin_centroids_all = df_bin_centroids, num_bins_x = num_bins_x,
                     df_bin_centroids_low = df_bin_centroids_low)
\end{verbatim}

@@

\begin{verbatim}
benchmark <- find_benchmark_value(.data = distance, distance_col = "distance")
benchmark <- 3
\end{verbatim}

@@

\begin{verbatim}
trimesh_gr <- colour_long_edges(.data = distance, benchmark_value = benchmark,
                                triangular_object = tr1_object, distance_col = "distance")

@@

\begin{verbatim}
trimesh_removed <- remove_long_edges(.data = distance, benchmark_value = benchmark,
                                     triangular_object = tr1_object, distance_col = "distance")
trimesh_removed
\end{verbatim}

@@

@@

All functions have tests written and implemented using the \CRANpkg{testthat} (Wickham 2011) in R.

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-41-1.pdf}

@@

@@

\begin{verbatim}
#> Calculating PHATE...
#>   Running PHATE on 824 observations and 8 variables.
#>   Calculating graph and diffusion operator...
#>     Calculating KNN search...
#>     Calculating affinities...
#>   Calculated graph and diffusion operator in 0.01 seconds.
#>   Calculating optimal t...
#>     Automatically selected t = 22
#>   Calculated optimal t in 0.49 seconds.
#>   Calculating diffusion potential...
#>   Calculated diffusion potential in 0.38 seconds.
#>   Calculating metric MDS...
#>   Calculated metric MDS in 7.83 seconds.
#> Calculated PHATE in 8.72 seconds.
\end{verbatim}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-47-1.pdf}

\begin{verbatim}
num_bins_x <- calculate_effective_x_bins(.data = tSNE_data, x = "tSNE1", hex_size = NA)
\end{verbatim}

\begin{verbatim}
num_bins_y <- calculate_effective_y_bins(.data = tSNE_data, y = "tSNE2", hex_size = NA)
num_bins_y
\end{verbatim}

\begin{verbatim}
#> [1] 38
\end{verbatim}

@@

df_with_std_counts <- compute_std_counts(nldr_df = tSNE_data_with_id)

@@

\begin{verbatim}
#>               x             y hexID std_counts
#> 1   -26.9783746  -3.336399929   552     0.6875
#> 2   -25.0331153  -3.336399929   553     0.3750
#> 3   -26.0057449  -1.663988875   582     0.2500
#> 4   -23.0878560  -6.681222036   496     0.5625
#> 5   -24.0604856  -5.008810982   525     0.3125
#> 6   -23.0878560  -3.336399929   554     0.3125
#> 7   -24.0604856  -1.663988875   583     0.1875
#> 8   -23.0878560   0.008422179   612     0.0625
#> 9   -22.1152263  -8.353633090   468     0.0625
#> 10  -22.1152263  -5.008810982   526     0.0625
#> 11  -19.1973374 -13.370866252   382     0.0625
#> 12  -19.1973374  16.732532718   904     0.1250
#> 13  -19.1973374  20.077354826   962     0.1250
#> 14  -17.2520781 -13.370866252   383     0.1875
#> 15  -18.2247077 -11.698455198   412     0.2500
#> 16  -17.2520781  16.732532718   905     0.1250
#> 17  -18.2247077  18.404943772   934     0.6875
#> 18  -17.2520781  20.077354826   963     0.1875
#> 19  -16.2794484 -18.388099413   297     0.6250
#> 20  -15.3068188 -16.715688359   326     0.2500
#> 21  -16.2794484 -15.043277306   355     0.3750
#> 22  -14.3341891 -18.388099413   298     0.0625
#> 23  -13.3615595 -16.715688359   327     0.1875
#> 24  -14.3341891 -15.043277306   356     0.0625
#> 25  -14.3341891  -5.008810982   530     0.0625
#> 26  -13.3615595  -3.336399929   559     0.3125
#> 27  -13.3615595  20.077354826   965     0.2500
#> 28  -14.3341891  21.749765879   994     0.0625
#> 29  -13.3615595  23.422176933  1023     0.5000
#> 30  -12.3889298  -8.353633090   473     0.1875
#> 31  -12.3889298  -5.008810982   531     0.0625
#> 32  -11.4163002  -3.336399929   560     0.1250
#> 33  -12.3889298  -1.663988875   589     0.1250
#> 34  -12.3889298  18.404943772   937     0.0625
#> 35  -11.4163002  20.077354826   966     0.5625
#> 36  -12.3889298  21.749765879   995     0.1875
#> 37  -11.4163002  23.422176933  1024     0.1875
#> 38  -12.3889298  25.094587987  1053     0.3125
#> 39  -11.4163002  26.766999041  1082     0.0625
#> 40   -9.4710409 -13.370866252   387     0.1875
#> 41  -10.4436705 -11.698455198   416     0.2500
#> 42   -9.4710409 -10.026044144   445     0.2500
#> 43  -10.4436705  -8.353633090   474     0.2500
#> 44   -9.4710409  -6.681222036   503     0.0625
#> 45   -9.4710409   6.698066395   735     0.1875
#> 46   -9.4710409  10.042888502   793     0.0625
#> 47   -9.4710409  16.732532718   909     0.0625
#> 48  -10.4436705  18.404943772   938     0.3125
#> 49   -9.4710409  20.077354826   967     0.2500
#> 50  -10.4436705  21.749765879   996     0.2500
#> 51   -9.4710409  23.422176933  1025     0.1875
#> 52  -10.4436705  25.094587987  1054     0.1875
#> 53   -9.4710409  26.766999041  1083     0.1875
#> 54   -7.5257816 -20.060510467   272     0.3750
#> 55   -8.4984112 -18.388099413   301     0.0625
#> 56   -7.5257816 -16.715688359   330     0.1250
#> 57   -8.4984112 -15.043277306   359     0.3125
#> 58   -7.5257816 -13.370866252   388     0.2500
#> 59   -8.4984112 -11.698455198   417     0.1875
#> 60   -7.5257816 -10.026044144   446     0.4375
#> 61   -8.4984112  -8.353633090   475     0.3750
#> 62   -7.5257816  -6.681222036   504     0.3125
#> 63   -8.4984112  -5.008810982   533     0.0625
#> 64   -7.5257816  -3.336399929   562     0.1250
#> 65   -7.5257816   0.008422179   620     0.1875
#> 66   -7.5257816   3.353244287   678     0.1250
#> 67   -8.4984112   5.025655341   707     0.1250
#> 68   -8.4984112   8.370477449   765     0.3750
#> 69   -7.5257816  10.042888502   794     0.0625
#> 70   -8.4984112  18.404943772   939     0.1250
#> 71   -7.5257816  20.077354826   968     0.1250
#> 72   -8.4984112  21.749765879   997     0.1875
#> 73   -7.5257816  23.422176933  1026     0.1250
#> 74   -6.5531519 -18.388099413   302     0.1250
#> 75   -5.5805223 -16.715688359   331     0.1250
#> 76   -6.5531519 -15.043277306   360     0.3125
#> 77   -5.5805223 -13.370866252   389     0.3125
#> 78   -6.5531519 -11.698455198   418     0.0625
#> 79   -5.5805223 -10.026044144   447     0.1875
#> 80   -6.5531519  -8.353633090   476     0.3750
#> 81   -5.5805223  -6.681222036   505     0.1250
#> 82   -6.5531519  -5.008810982   534     0.1875
#> 83   -6.5531519  -1.663988875   592     0.0625
#> 84   -5.5805223   0.008422179   621     0.0625
#> 85   -6.5531519   5.025655341   708     0.1875
#> 86   -5.5805223   6.698066395   737     0.2500
#> 87   -6.5531519   8.370477449   766     0.0625
#> 88   -5.5805223  10.042888502   795     0.3125
#> 89   -5.5805223  13.387710610   853     0.0625
#> 90   -5.5805223  16.732532718   911     0.1250
#> 91   -6.5531519  18.404943772   940     0.1250
#> 92   -3.6352630 -16.715688359   332     0.1875
#> 93   -4.6078926 -15.043277306   361     0.1875
#> 94   -3.6352630 -13.370866252   390     0.1250
#> 95   -4.6078926 -11.698455198   419     0.1875
#> 96   -3.6352630 -10.026044144   448     0.1875
#> 97   -4.6078926  -8.353633090   477     0.3125
#> 98   -3.6352630  -6.681222036   506     0.3125
#> 99   -4.6078926  -5.008810982   535     0.1250
#> 100  -3.6352630   0.008422179   622     0.2500
#> 101  -3.6352630   6.698066395   738     0.2500
#> 102  -4.6078926   8.370477449   767     0.1250
#> 103  -3.6352630  10.042888502   796     0.1875
#> 104  -4.6078926  11.715299556   825     0.0625
#> 105  -3.6352630  13.387710610   854     0.2500
#> 106  -4.6078926  15.060121664   883     0.1250
#> 107  -1.6900037 -33.439798898    43     0.0625
#> 108  -2.6626333 -18.388099413   304     0.0625
#> 109  -1.6900037 -16.715688359   333     0.1250
#> 110  -2.6626333 -15.043277306   362     0.2500
#> 111  -1.6900037 -13.370866252   391     0.3125
#> 112  -2.6626333 -11.698455198   420     0.1250
#> 113  -1.6900037 -10.026044144   449     0.2500
#> 114  -2.6626333  -8.353633090   478     0.2500
#> 115  -1.6900037  -6.681222036   507     0.3750
#> 116  -2.6626333  -5.008810982   536     0.1250
#> 117  -2.6626333  -1.663988875   594     0.4375
#> 118  -2.6626333   5.025655341   710     0.1250
#> 119  -1.6900037  10.042888502   797     0.0625
#> 120  -2.6626333  11.715299556   826     0.4375
#> 121  -1.6900037  13.387710610   855     0.1250
#> 122  -2.6626333  15.060121664   884     0.0625
#> 123   0.2552556 -33.439798898    44     1.0000
#> 124   0.2552556 -13.370866252   392     0.1875
#> 125  -0.7173740 -11.698455198   421     0.1250
#> 126   0.2552556 -10.026044144   450     0.1250
#> 127  -0.7173740  -8.353633090   479     0.0625
#> 128  -0.7173740   1.680833233   653     0.0625
#> 129   0.2552556   3.353244287   682     0.5000
#> 130  -0.7173740   5.025655341   711     0.3125
#> 131  -0.7173740   8.370477449   769     0.1875
#> 132   0.2552556  10.042888502   798     0.2500
#> 133  -0.7173740  11.715299556   827     0.1250
#> 134  -0.7173740  15.060121664   885     0.1875
#> 135   0.2552556  16.732532718   914     0.1875
#> 136   1.2278853 -35.112209952    16     0.0625
#> 137   2.2005149 -33.439798898    45     0.3750
#> 138   1.2278853 -31.767387844    74     0.0625
#> 139   2.2005149 -30.094976790   103     0.6250
#> 140   1.2278853 -28.422565737   132     0.0625
#> 141   2.2005149 -26.750154683   161     0.1250
#> 142   1.2278853 -25.077743629   190     0.0625
#> 143   2.2005149 -23.405332575   219     0.1250
#> 144   1.2278853 -21.732921521   248     0.0625
#> 145   1.2278853 -18.388099413   306     0.0625
#> 146   2.2005149 -16.715688359   335     0.0625
#> 147   1.2278853 -15.043277306   364     0.3125
#> 148   1.2278853   1.680833233   654     0.3750
#> 149   2.2005149   3.353244287   683     0.1875
#> 150   1.2278853   5.025655341   712     0.2500
#> 151   2.2005149   6.698066395   741     0.1250
#> 152   1.2278853   8.370477449   770     0.0625
#> 153   2.2005149  10.042888502   799     0.1875
#> 154   1.2278853  11.715299556   828     0.3750
#> 155   2.2005149  13.387710610   857     0.1875
#> 156   1.2278853  15.060121664   886     0.3750
#> 157   2.2005149  16.732532718   915     0.1875
#> 158   1.2278853  18.404943772   944     0.0625
#> 159   3.1731446 -31.767387844    75     0.0625
#> 160   4.1457742 -30.094976790   104     0.2500
#> 161   3.1731446 -28.422565737   133     0.3750
#> 162   3.1731446 -25.077743629   191     0.6875
#> 163   4.1457742 -23.405332575   220     0.0625
#> 164   3.1731446  -8.353633090   481     0.1250
#> 165   3.1731446   1.680833233   655     0.1875
#> 166   3.1731446   5.025655341   713     0.0625
#> 167   3.1731446   8.370477449   771     0.1250
#> 168   4.1457742  10.042888502   800     0.1250
#> 169   3.1731446  11.715299556   829     0.1875
#> 170   4.1457742  13.387710610   858     0.1250
#> 171   3.1731446  15.060121664   887     0.1250
#> 172   5.1184039 -25.077743629   192     0.1250
#> 173   6.0910335   0.008422179   627     0.1250
#> 174   6.0910335   3.353244287   685     0.0625
#> 175   6.0910335   6.698066395   743     0.1250
#> 176   6.0910335  10.042888502   801     0.1250
#> 177   6.0910335  13.387710610   859     0.1250
#> 178   8.0362928   0.008422179   628     0.0625
#> 179   7.0636632   1.680833233   657     0.1250
#> 180   8.0362928   3.353244287   686     0.3125
#> 181   7.0636632   5.025655341   715     0.2500
#> 182   8.0362928   6.698066395   744     0.1250
#> 183   7.0636632   8.370477449   773     0.0625
#> 184   8.0362928  10.042888502   802     0.3125
#> 185   7.0636632  11.715299556   831     0.0625
#> 186   8.0362928  13.387710610   860     0.0625
#> 187   7.0636632  15.060121664   889     0.2500
#> 188   8.0362928  16.732532718   918     0.1875
#> 189   7.0636632  18.404943772   947     0.0625
#> 190   9.9815521   0.008422179   629     0.0625
#> 191   9.0089225   1.680833233   658     0.1250
#> 192   9.9815521   3.353244287   687     0.1250
#> 193   9.0089225   5.025655341   716     0.1250
#> 194   9.9815521   6.698066395   745     0.1250
#> 195   9.0089225   8.370477449   774     0.1875
#> 196   9.9815521  10.042888502   803     0.1875
#> 197   9.0089225  11.715299556   832     0.2500
#> 198   9.9815521  13.387710610   861     0.0625
#> 199   9.0089225  15.060121664   890     0.2500
#> 200   9.9815521  16.732532718   919     0.0625
#> 201  11.9268114   0.008422179   630     0.1250
#> 202  10.9541818   1.680833233   659     0.3125
#> 203  11.9268114   3.353244287   688     0.2500
#> 204  11.9268114   6.698066395   746     0.1875
#> 205  11.9268114  10.042888502   804     0.0625
#> 206  10.9541818  11.715299556   833     0.1875
#> 207  11.9268114  13.387710610   862     0.1250
#> 208  10.9541818  15.060121664   891     0.1875
#> 209  13.8720707  -3.336399929   573     0.2500
#> 210  12.8994411  -1.663988875   602     0.1250
#> 211  13.8720707   0.008422179   631     0.0625
#> 212  12.8994411   1.680833233   660     0.1250
#> 213  13.8720707   3.353244287   689     0.1250
#> 214  12.8994411   5.025655341   718     0.2500
#> 215  12.8994411   8.370477449   776     0.0625
#> 216  13.8720707  10.042888502   805     0.2500
#> 217  12.8994411  11.715299556   834     0.3750
#> 218  13.8720707  13.387710610   863     0.1250
#> 219  12.8994411  15.060121664   892     0.3750
#> 220  14.8447004  -5.008810982   545     0.4375
#> 221  15.8173300  -3.336399929   574     0.1250
#> 222  15.8173300   0.008422179   632     0.3750
#> 223  14.8447004   5.025655341   719     0.1875
#> 224  14.8447004   8.370477449   777     0.0625
#> 225  15.8173300  10.042888502   806     0.1250
#> 226  14.8447004  11.715299556   835     0.2500
#> 227  14.8447004  15.060121664   893     0.0625
#> 228  16.7899597  -5.008810982   546     0.0625
#> 229  17.7625893  -3.336399929   575     0.0625
#> 230  16.7899597  -1.663988875   604     0.1875
#> 231  17.7625893   0.008422179   633     0.2500
#> 232  17.7625893   3.353244287   691     0.1250
#> 233  16.7899597   5.025655341   720     0.0625
#> 234  17.7625893   6.698066395   749     0.0625
#> 235  17.7625893  10.042888502   807     0.0625
#> 236  16.7899597  11.715299556   836     0.0625
#> 237  19.7078486  -3.336399929   576     0.1250
#> 238  18.7352190  -1.663988875   605     0.3750
#> 239  19.7078486   0.008422179   634     0.2500
#> 240  18.7352190   1.680833233   663     0.4375
#> 241  19.7078486   3.353244287   692     0.3125
#> 242  18.7352190   5.025655341   721     0.0625
#> 243  19.7078486   6.698066395   750     0.2500
#> 244  18.7352190   8.370477449   779     0.1875
#> 245  19.7078486  10.042888502   808     0.1875
#> 246  20.6804783  -1.663988875   606     0.3125
#> 247  21.6531079   0.008422179   635     0.0625
#> 248  20.6804783   1.680833233   664     0.1875
#> 249  21.6531079   3.353244287   693     0.2500
#> 250  21.6531079   6.698066395   751     0.2500
#> 251  20.6804783   8.370477449   780     0.1875
#> 252  21.6531079  10.042888502   809     0.5000
#> 253  20.6804783  11.715299556   838     0.0625
#> 254  22.6257376  -1.663988875   607     0.1250
#> 255  23.5983672   0.008422179   636     0.1875
#> 256  22.6257376   1.680833233   665     0.0625
#> 257  23.5983672   3.353244287   694     0.1875
#> 258  23.5983672   6.698066395   752     0.1875
#> 259  22.6257376   8.370477449   781     0.1250
#> 260  24.5709969   1.680833233   666     0.3750
#> 261  24.5709969   5.025655341   724     0.1875
#> 262  25.5436265   6.698066395   753     0.0625
#> 263  24.5709969   8.370477449   782     0.2500
#> 264  26.5162562   1.680833233   667     0.1875
\end{verbatim}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-testthat}{}}%
Wickham, Hadley. 2011. {``Testthat: Get Started with Testing.''} \emph{The R Journal} 3: 5--10. \url{https://journal.r-project.org/archive/2011-1/RJournal_2011-1_Wickham.pdf}.

\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
Xie, Yihui. 2015. \emph{Dynamic Documents with {R} and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{https://yihui.name/knitr/}.
